Robotic Grasping in Clutter: Using a Hierarchy of Supervisors with (Deep) Learning from Demonstrations

### 2016-03-18 paper.tex
anca's feedback incoporated

\title{Robotic Grasping in Clutter: Using a Hierarchy of Supervisors for \adnote{(Deep)} Learning from Demonstrations\adnote{I would remove deep but if you really want to keep it put it in parens? deep is not central to this and it pigeonholes you}}

@@

\adnote{In particular, while model-based planners might not yet capture the full physical interaction among all objects, it is wasteful to completely throw them away and learn with an expert supervisor from scratch. Thus, at the lowest lever of the hierarchy, we use a motion planner on an \emph{relaxed} version of the problem. In our grasping application, we use a planner that ignores the clutter but can leverage knowledge of the kinematics and the goal.}
The next supervisor in the hierarchy are crowdsource workers on Amazan Mechnical Turker\adnote{Turk not Turker}. Then finally the robot is trained with a Phd student in robotics, who is an expert human supervisor. Examples of the resulting learned grasping in clutter policy can be seen in Fig. \ref{fig:teaser}.

@@

 \subsubsection{Step 2}
The second step  DAgger rolls out their policies, $\pi_{\theta_{k}}$, to sample states that are likely under $p(\bx|\theta_{k})$.  For every state visited, DAgger requests the supervisor to provide the appropriate control/label. Formally, for a given sampled trajectory  $\hat{\tau} = (\bx_0,\bu_0,...,\bx_T,\bu_T )$, the supervisor provides labels $\tilde{\bu}_t$, where $\tilde{\bu}_t \sim \tilde{\pi}(\bx_t) + \epsilon$, where $\epsilon$ is a small zero mean noise term, for $t\in \{0, \ldots, T\}$.
The states and labeled controls are then aggregated into the next data set of demonstrations $\mathcal{D}_{k+1}$:
$$D_{k+1}=\mathcal{D}_k \cup \{(\bx_t,\tilde{\bu_t})\|t\in\{0,\ldots,T\}\} $$
{\color{blue}FP: can we just have a neat algorithm box here?}
%\fpnote{terms such as aggregated etc would be much clearer if we just refer to a particular line in the algorithm}

@@

\adnote{start with a description of what we want to test: the main thing is that hierarchy maintains performance compared to expert but reduces cost; also mention secondary tings}
For an experiment in the grasping in clutter domain, we are interested in training a Zymark robot to perform a grasping in clutter task on image data taken from a Logitech C270 camera. Examples of images from the camera can be seen in Fig. \ref{fig:teaser}.

@@

We first test  that using a hierarchy of supervisors can reduce total cost needed to train a policy, but still maintain similar performance .  We compare having an analytical only supervisor for a fixed amount of data \adnote{to having only an expert, and to having the hierarchy of both}. The non-hierarchical policies trained with the expert supervisor only for 160 demonstrations or only the MPIO supervisor for 160 demonstrations.  The policy trained with a hierarchical supervisor first receives  100 demonstrations from the MPIO supervisor and  60 demonstrations from the expert supervisor.

\adnote{We hypothesized that the hierarchy will perform on par with the expert while reducing cost.}

Our results, shown in Fig. \ref{fig:perf_results}, \adnote{support this hypothesis. The policy trained... achieved ...}are the policy trained with just the MPIO supervisor achieves a score of $0.325\%$, the policy trained with just an expert achieves $0.54\%$ and the policy trained with a hierarchy of supervisor achieves $0.55\%$.  Thus, the hierarchical supervisor and expert supervisor achieve approximately the same performance. However,training with a hierarchical supervisor yields a $40\%$ reduction in cost incurred compared to the policy trained with only an expert supervisor.

Thus demonstrating that by using a hierarchy of supervisors, we can reduce the cost of training a policy and achieve similar performance to the \adnote{expert.}

\subsection{Quality of Crowdsourced Supervisor}
We next evaluate the potential of a  crowdsourced supervisor for a being part of the hierarchy. Thus, we perform an experiment using the AMT platform described in Sec. \ref{sec:hier}. We  test how well a crowdosurce supervisor performs as part of a hierarchy of supervisors, \adnote{this sentence is not ending here?}we had a policy train with 100  demonstrations  from the MPIO supervisor , then had 60 demonstrations provided by AMT workers. We also compare how well the crowdsource supervisors performs just as well as a single supervisor,  by having them provide all 160 demonstrations \mlnote{we need to test this policy tomorrow}\adnote{ok good so hopefully we will get that mpio->cs as good as cs}

@@

\caption{\footnotesize The performance of each policy trained with a different data management strategy is reported. The bar graphs shows the breakdown in terms of situations the policy encountered on the test set. Each policy was trained with the MPIO to Human Expert hierarchical supervisor. From left to right is the following data management strategies: Dataset Aggregation, Weight Transfer and Regularization. Regularization achieves the highest performing score of (0.18) }
\vspace*{-20pt}
\label{fig:cost_result}
\end{figure}

@@

>>>>

\title{Robotic Grasping in Clutter: Using a Hierarchy of Supervisors with  (Deep) Learning from Demonstrations}

@@

In particular, while model-based planners might not yet capture the full physical interaction among all objects, it can be wasteful to not leverage them and learn with an expert supervisor from scratch. Thus, at the lowest lever of the hierarchy, we use a motion planner on an relaxed version of the problem. In our grasping application, we use a planner that ignores the obstacles but can leverage knowledge of the kinematics and the goal.
The next supervisor in the hierarchy are crowdsource workers on Amazan Mechnical Turk. Then finally the robot is trained with a Phd student in robotics, who is an expert human supervisor. Examples of the resulting learned grasping in clutter policy can be seen in Fig. \ref{fig:teaser}.

@@

 \subsubsection{Step 2}
The second step  DAgger rolls out their policies, $\pi_{\theta_{k}}$, to sample states that are likely under $p(\bx|\theta_{k})$.  For every state visited, DAgger requests the supervisor to provide the appropriate control/label. Formally, for a given sampled trajectory  $\hat{\tau} = (\bx_0,\bu_0,...,\bx_T,\bu_T )$, the supervisor provides labels $\tilde{\bu}_t$, where $\tilde{\bu}_t \sim \tilde{\pi}(\bx_t) + \epsilon$, where $\epsilon$ is a small zero mean noise term, for $t\in \{0, \ldots, T\}$.
The states and labeled controls are then aggregated into the next data set of demonstrations $\mathcal{D}_{k+1}$:
$$D_{k+1}=\mathcal{D}_k \cup \{(\bx_t,\tilde{\bu_t})\|t\in\{0,\ldots,T\}\} $$

%\fpnote{terms such as aggregated etc would be much clearer if we just refer to a particular line in the algorithm}

@@

In this section, we first describe the grasping in clutter experimental setup. Then we test how the supervisor hierarchy performs versus not leveraging a hierarchy. We then test how high of Quality the CrowdSource supervisor is. Then, we experiment with different ways to advance in the hierarchy. Finally, we look at using all three supervisors and to train a robot for the grasping in clutter task.

\subsection{Experimental Setup}
For experimenting in the grasping in clutter domain, we are interested in training a Zymark robot to perform a grasping in clutter task on image data taken from a Logitech C270 camera. Examples of images from the camera can be seen in Fig. \ref{fig:teaser}.

@@

We first test  that using a hierarchy of supervisors can reduce total cost needed to train a policy, but still maintain similar performance .  We compare having only a MPIO Supervisor for a fixed amount of data to having only an Human Expert, and to having the hierarchy of both . The non-hierarchical policies trained with the human expert supervisor only for 160 demonstrations or only the MPIO supervisor for 160 demonstrations.  The policy trained with a hierarchical supervisor first receives  100 demonstrations from the MPIO supervisor and  60 demonstrations from the expert supervisor.

Our results, shown in Fig. \ref{fig:perf_results}, are the policy trained with just the MPIO supervisor achieves a score of $0.325\%$, the policy trained with just an expert achieves $0.54\%$ and the policy trained with a hierarchy of supervisor achieves $0.55\%$.  Thus, the hierarchical supervisor and expert supervisor achieve approximately the same performance. However,training with a hierarchical supervisor yields a $40\%$ reduction in cost incurred compared to the policy trained with only an expert supervisor.

Thus demonstrating that by using a hierarchy of supervisors, we can reduce the cost of training a policy and achieve similar performance to the Human Expert Supervisor.

\caption{\footnotesize The performance of each policy trained with a different data management strategy is reported. The bar graphs shows the breakdown in terms of situations the policy encountered on the test set. Each policy was trained with the MPIO to Human Expert hierarchical supervisor. From left to right is the following data management strategies: Dataset Aggregation, Weight Transfer and Regularization. Regularization achieves the highest performing score of (0.18) }
\label{fig:cost_result}
\end{figure}

\subsection{Quality of Crowdsourced Supervisor}
We next evaluate the potential of a  crowdsourced supervisor for a being part of the hierarchy. Thus, we perform an experiment using the AMT platform described in Sec. \ref{sec:hier}. We  first test how well a crowdosurce supervisor performs as part of a hierarchy of supervisors. We trained a policy with 100  demonstrations  from the MPIO supervisor , then had 60 demonstrations provided by AMT workers. We also compare how well the crowdsource supervisors performs just as well as a single supervisor,  by having them provide all 160 demonstrations.

@@

@@

\begin{figure}[t]
\includegraphics{f_figs/big_data.eps}

\caption{ \footnotesize The performance and cost of each policy trained with a supervisor is reported. The bar graphs shows the breakdown in terms of situations the policy encountered on the test set. The top row corresponds to policies only trained with one supervisor: MPIO, Crowdsourced or Human Expert. The bottom corresponds to policies trained with a hierarchy of supervisors: MPIO and Crowdsource, MPIO and Human Expert, MPIO, Crowdsourced and Human Expert. The final bottom right plot demonstrates the full hierarchy, which achieves the best performance (0.8).   }
\vspace*{-20pt}
\label{fig:big_data}
\end{figure}
